---
title: "La1"
author: "Hariprasad H N"
date: "2024-01-27"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


packages_to_install <- c("ggplot2", "dplyr", "tidyr", "readr", "lubridate", "stringr", "knitr", "rmarkdown")
install.packages(packages_to_install)
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)


```{r}
# Loading the dataset
my_data <- read.csv("C:/Users/harsh/Music/edal1/globalterrorismdb_0718dist.csv")


# Data Inspection
head(my_data) # View the first 6 rows of the data frame
tail(my_data) # View the last 6 rows of the data frame
View(my_data) # Open a data frame in a spreadsheet-like window
str(my_data) # Display the structure of the data frame
summary(my_data) # Provide a summary of the data frame
dim(my_data) # Return the dimensions of the data frame
nrow(my_data) # Get the number of rows
ncol(my_data) # Get the number of columns
names(my_data) # Get the column names
colnames(my_data) # Get the column names (synonym to names())
rownames(my_data) # Get the row names
class(my_data) # Get the class of the data frame
typeof(my_data) # Get the type of the data frame
levels(my_data$variable) # Get the levels of a factor variable
unique(my_data$variable) # Get unique values of a column
  

# Data Wrangling with dplyr
library(dplyr) # Load the dplyr package for data manipulation
my_data_filtered <- filter(my_data, iyear >= 2000) # Filter rows based on a condition
my_data_selected <- select(my_data, iyear, nkill) # Select specific columns
my_data_mutated <- mutate(my_data, casualties = nkill + nwound) # Create a new column
my_data_summarised <- summarise(my_data, total_kills = sum(nkill, na.rm = TRUE)) # Summarise data
my_data_grouped <- group_by(my_data, iyear) # Group data by year


# Statistical Analysis


# Plotting incidents by year

# Replace '1year' with the actual year column name


```{r year-ggplot}
ggplot(my_data, aes(x = iyear)) + 
  geom_bar() +
  labs(title = "Incidents by Year", x = "Year", y = "Number of Incidents")



```{r year-histogram}
# Histogram of incidents by year
ggplot(my_data, aes(x = iyear)) + 
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Incidents by Year",
       x = "Year",
       y = "Frequency") +
  theme_minimal()
mean_kills <- mean(my_data$nkill, na.rm = TRUE) # Calculate mean of kills
median_kills <- median(my_data$nkill, na.rm = TRUE) # Calculate median of kills
sd_kills <- sd(my_data$nkill, na.rm = TRUE) # Calculate standard deviation of kills
var_kills <- var(my_data$nkill, na.rm = TRUE) # Calculate variance of kills
cor_kills_wound <- cor(my_data$nkill, my_data$nwound, use = "complete.obs") # Correlation between kills 

```{r glm-model}
# Generalized Linear Modeling
glm_model <- glm(success ~ nkill + nwound, family = binomial, data = my_data)
summary(glm_model) # Summarize the GLM
# T-Test
ttest_result <- t.test(nkill ~ success, data = my_data)
ttest_result # Display the t-test result
# Chi-Squared Test Example
# Replace 'attacktype1' and 'weaptype1' with the actual column names from your dataset
chisq_result <- chisq.test(table(my_data$attacktype1, my_data$weaptype1))
chisq_result # Display the chi-squared test result




